Evolution of ORM Systems: Formal Foundations

### 2013-01-16 doc/description.tex
application consistency + fixed mistake from last commit

The software has to be in consistent state so its users could have benefit from its usage. The state of the software is defined to communicate the sate of the software to its user. The components of a software (application and database) are transformed likewise, thus the state is defined for them too.
\begin{align*}
 	\mathbf{state} = Consistent\; s \: | \: Inconsistent \; s,  \\	s \lhd Software \vee s \lh Application \vee s \lhd Database
\end{align*}
Before the definition of the software consistency is provided, the notation of function transcription has to be introduced. Usually the definition of a function consists of two parts - an effect of the function and conditions when the effect occurs We decide to use following transcription, to simplify the notation and to improve understanding of functions:
\begin{align*}
f(x) =   \inference{conditions}{effect}
\end{align*}
The function querying the state (it means consistency) of a software is defined as:
\begin{align*}
 	\mathbf{consistent} : State \rightarrow Boolean \\
 	consistent(s) = \begin{cases}
 		\inference{s = Consistent(s)}{true}\\\\
 		\inference{s = Inconsistent(s)}{false}\\
 \end{cases}\\
 s \lhd State
\end{align*}
The consistency of application and database is discussed later in this paper. The definition of software state only is provided:
\begin{align*}
	\mathbf{state} : Software \rightarrow State \\
	state(s) = \begin{cases}
 		\inference{consistent(application(s)) \wedge \\ consistent(database(s)) \\ \wedge \rho(application(s)) = database(s)}{Consistent \; s}\\ \\
 		\inference{otherwise}{Inconsistent \; s}
 	\end{cases} \\ \\
\end{align*}

@@

\subsubsection{Application consistency}

>>>>

The software has to be in consistent state so its users could have benefit from its usage. The state of the software is defined to communicate the sate of the software to its user. The components of a software (application and database) are transformed likewise, thus the state is defined for them too.
\begin{align*}
 	\mathbf{state} = Consistent\; s \: | \: Inconsistent \; s,  \\	s \lhd Software \vee s \lh Application \vee s \lhd Database
\end{align*}
Before the definition of the software consistency is provided, the notation of function transcription has to be introduced. Usually the definition of a function consists of two parts - an effect of the function and conditions when the effect occurs We decide to use following transcription, to simplify the notation and to improve understanding of functions:
\begin{align*}
f(x) =   \inference{conditions}{effect}
\end{align*}
The function querying the state (it means consistency) of a software is defined as:
\begin{align*}
 	\mathbf{consistent} : State \rightarrow Boolean \\
 	consistent(s) = \begin{cases}
 		\inference{s = Consistent(s)}{true}\\\\
 		\inference{s = Inconsistent(s)}{false}\\
 \end{cases}\\
 s \lhd State
\end{align*}
The consistency of application and database is discussed later in this paper. The definition of software state only is provided:
\begin{align*}
	\mathbf{state} : Software \rightarrow State \\
	state(s) = \begin{cases}
 		\inference{consistent(application(s)) \wedge \\ consistent(database(s)) \\ \wedge \rho(application(s)) = database(s)}{Consistent \; s}\\ \\
 		\inference{otherwise}{Inconsistent \; s}
 	\end{cases} \\ 
 	s \lhd Software
\end{align*}

@@

\subsubsection{Application consistency}
The application consistency is based on the structural consistency of its model. Violation of structural consistency are name collisions and non-existing references in associations. The state of an application is:
\begin{align*}
	state(a) = \begin{cases}
	\inference{\forall c_1, c_2 \in classes(a) : name(c_1) \neq name(c_2) \\ \wedge \forall p_1, p_2 \in properties(c_1) : name(p_1) \neq name(p_2) \\ \wedge \forall a_1, a_2 \in associations(c_1) : name(a_1) \neq name (a_2) \\ \wedge \forall a \in associations(c_1) : \exists c \in classes(a) \wedge name(c) = reference(a) }{Consistent \; a}\\\\
 	Inconsistent \; a
 	\end{cases}\\
	a \lhd Application
\end{align*}
